Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex
split up some definitions

We now introduce the standard Boolean functions. 
\begin{definition}
 The AND function takes in 2 Boolean inputs, and returns a 1 if and only if both the input values are 1. We will use $\vee$ to denote AND. The OR function, that takes in 2 Boolean inputs, and returns a 0 if and only if both input values are set to 0. We will use $\wedge$ to denote OR. The NOT function takes in 1 Boolean input; it returns a 1 if and only if the input value is a 0. 
 \end{definition}
 If we think of associating 0 with ``false" and 1 with '``true", then the AND function returns ``true" if both inputs are ``true", and the OR function returns ``true" if at least one input is true. We can make more complicated Boolean functions with more than 2 inputs and compositions of these inputs.

>>>>

We now introduce the standard Boolean functions. 
\begin{definition}
 The AND function takes in 2 Boolean inputs, and returns a 1 if and only if both the input values are 1. We will use $\vee$ to denote AND.
\end{definition}
\begin{definition}
The OR function, that takes in 2 Boolean inputs, and returns a 0 if and only if both input values are set to 0. We will use $\wedge$ to denote OR.
\end{definition}
\begin{definition}
The NOT function takes in 1 Boolean input; it returns a 1 if and only if the input value is a 0. We will use $\neg$ to denote NOT.
 \end{definition}
 If we think of associating 0 with ``false" and 1 with '``true", then the AND function returns ``true" if both inputs are ``true", and the OR function returns ``true" if at least one input is true. We can make more complicated Boolean functions with more than 2 inputs and compositions of these inputs.
